---
title: "Coolest paper ever!"
author:
- name: Vidushi Kataria
  affiliation: '1'
  corresponding: no
  email: vk412@scarletmail.rutgers.edu
  role:
  - Conceptualization
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"

affiliation:
  - id : "1"
  - institution : "Rutgers University"
  
shorttitle: Title
output:
  papaja::apa6_docx: default
  
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: "One or two sentences providing a **basic introduction** to the field,  comprehensible
  to a scientist in any discipline.\nTwo to three sentences of **more detailed background**,
  comprehensible  to scientists in related disciplines.\nOne sentence clearly stating
  the **general problem** being addressed by  this particular study.\nOne sentence
  summarizing the main result (with the words \"**here we show**\" or their equivalent).\nTwo
  or three sentences explaining what the **main result** reveals in direct comparison
  to what was thought to be the case previously, or how the  main result adds to previous
  knowledge.\nOne or two sentences to put the results into a more **general context**.\nTwo
  or three sentences to provide a **broader perspective**, readily comprehensible
  to a scientist in any discipline.\n\n<!-- https://tinyurl.com/ybremelq -->\n"
keywords: keywords
wordcount: X
bibliography: "r-references.bib"
floatsintext: no
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
classoption: man
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results


(ref:chick-caption) Each chick was weighed every other day from birth to day 20 and on day 21. This plot shows the weight of each chick (y-axis) for each day they were measured (x-axis). Each point is one measurement.
```{r chick-plot, fig.cap="(ref:chick-caption)"}
ChickWeight %>%
  ggplot(aes(y = weight, x = Time)) +
  geom_point()
```


```{r chick-plot-red, fig.cap="This is my red chick weight"}
ChickWeight %>%
  ggplot(aes(y = weight, x = Time)) +
  geom_point(color = "red")
```



# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
