---
title: "D2SC: Weekly Assignments"
date: "2024-9-10"
author: "Vidushi Kataria"
output: html_notebook
---
# Initial Heading
```{r}
library(tidyverse)
```
# Week 1
Due to my previous programming experience and coursework using R, I knew to use library() to load the tidyverse package.

I did refer to this website, as it gave me a concise description between each function within tidyverse: https://www.tidyverse.org/packages/ 

I checked that it was working by using the command and return buttons on my keyboard to run the code. The console is able to tell me if the code successfully ran or had errors. 

```{r}
help("tidyverse")
```
tidyverse-package {tidyverse}	R Documentation
tidyverse: Easily Install and Load the 'Tidyverse'
Description
logo
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

Author(s)
Maintainer: Hadley Wickham hadley@rstudio.com

Other contributors:

RStudio [copyright holder, funder]

See Also
Useful links:

https://tidyverse.tidyverse.org

https://github.com/tidyverse/tidyverse

Report bugs at https://github.com/tidyverse/tidyverse/issues
